تخصیص منابع در شبکه‌های دسترسی رادیویی باز با برش‌دهی شبکه

### 2022-01-15 Latex/journal_v1/V3/pr.tex
simulation change
first commit for new git

\begin{figure}
  \centering
    \includegraphics[scale = 0.4]{draw1.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.
Assume we have preallocated slices serving these services;
Each Service $s\in \{1,2,3 \} $ consists of $U_{s}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_ \in \{1,23 \}$ consists of $K_{s}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ single-antenna RU that are shared between slices. All RUs $r \in \{1,2,...,R \}$
transmit signals cooperatively to all the UEs(RUs are in comp mode). Moreover, all RUs, have access to PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE requesting served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{r,u(s,i)}^{k} =  \frac{|p_{r,u(s,i)}^{k}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0 + I_{r,u(s,i)}^{k}},
\end{equation} 
where $p_{r,u(s,i)}^{k}$ represents the transmission power from o-RU $r$ to $i^{th}$ UE served at slice $s$ on PRB $k$. 
${\bold{h}_{r,u(s,i)}^{k}} \in \mathbb{C}^{J}$ is the vector of channel gain of a wireless link from 
$r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice. In addition, $\bold{w}_{r,u(s,i)}^{k} \in \mathbb{C}^{J}$ depicts the  transmit beamforming vector from $r^{th}$ RU to the $i^{th}$ UE in $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{r,u(s,i)}^{k} = {\bold{h}_{r,u(s,i)}^{k}}({\bold{h}_{r,u(s,i)}^{H \: k}} {\bold{h}_{r,u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $g_{u(s,i)}^r \in \{0,1\}$ is a binary variable that illustrates whether RU $r$ is mapped to the $i^{th}$ UE allocate to $s^{th}$ slice or not. 
Also, $BN_0$ denotes the power of Gaussian additive noise, and $I_{r,u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{r,u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(s,i)}^{k} g_{u(s,i)}^{r'}|^2}_{\text{(intra-slice interference)}}\\
&+ \underbrace{\sum_{\substack{n = 1 \\ n\neq s}}^{S}\sum_{l=1}^{{U}_s} \gamma_{2}  p_{u(n,l)}^{k}\sum_{\substack{r'=1 \\ r'\neq r}}^{R}|{\bold{h}_{r',u(s,i)}^{H \: k}} \bold{w}_{r',u(n,l)}^{k} g_{u(n,l)}^{r'}|^2}_{\text{(inter-slice interference)}}\\
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{r,u(s,i)}e^{k}_{r',u(s,l)}a_{u(s,i)}a_{u(s,l)}$
and $\gamma_{2} = e^{k}_{r,u(s,i)}e^{k}_{r',u(n,l)}a_{u(s,i)}a_{u(y,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{r,u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

>>>>

\begin{figure}
  \centering 
    %\includegraphics[scale = 0.4]{Drawing13.pdf}
    \includegraphics[scale = 0.4]{Drawing13.pdf}
  \caption{Network sliced ORAN system}
  \label{fig:c11}
\end{figure}

@@

In this section, first, we  present the system model. Then, we obtain achievable data rates and delays for the downlink (DL) of the ORAN system. Afterward, we discuss about the assignment of physical data center resources.
Finally, the main problem is expressed.
\subsection{System Model}
Suppose we have three service types includes mMTC, eMBB and URLLC which support different applications.
Assume we have preallocated slices serving these services;
So each service request $s$ served by its corresponding slice.
Each Service $s\in \{1,2,3 \} $ consists of $U_{s}$ request from the 
single-antenna UEs which require certain QoS to be able to use the requested program indicate service type).
There are different application request which fall into one of these service categories. Each application request requires specific QoS. Based on the request for the application and QoS, UE may be admitted and allocated to the resources.
Each slice $s_ \in \{1,2,3 \}$ consists of $K_{s}$ preallocated virtual resource blocks that are mapped to Physical Resource Blocks (PRBs), $M_s^{d}$ VNFs for the processing of O-DU, $M_s^{c}$ VNFs for the processing of O-CU-UP and $M_s^{u}$ VNFs for the processing of UPF.

@@

In addition, there are $R$ single-antenna RU that are shared between slices. 
All RUs $\{ r_i | i\in 1,2,...,R \}$
transmit signals cooperatively to all the UEs. 
Also $\mathcal{R} = \{ r_i | i\in 1,2,...,R \}$ depicts the set of o-RUs.
Moreover, all o-RUs, have access to all PRBs.
\subsection{The Achievable Rate}
The SNR of $i^{th}$ UE  served at slice $s$ on PRB $k$ is obtained from
\begin{equation}\label{eq2}
\rho_{u(s,i)}^{k} =  \frac{|p_{u(s,i)}^{k}{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k}}{BN_0 + I_{u(s,i)}^{k}},
\end{equation} 
where $p_{u(s,i)}^{k}$ represents the transmission power allocated by set of o-RUs $\mathcal{R}$ to $i^{th}$ UE requesting $s^{th}$ service on PRB $k$. 
${\bold{h}_{\mathcal{R},u(s,i)}^{k}} \in \mathbb{C}^{R}$ is the vector of channel gain of a wireless link from set of 
$\mathcal{R} = \{r\in 1,2,...,R\}$ O-RUs to the $i^{th}$ UE requesting $s^{th}$ service. In addition, $\bold{w}_{\mathcal{R},u(s,i)}^{k} \in \mathbb{C}^{R}$ depicts the  transmit beamforming vector from set of $\mathcal{R}$ o-RU to the $i^{th}$ UE served by $s^{th}$ slice that is the zero forcing beamforming vector to minimize the interference which is indicated as below
\begin{equation}
\bold{w}_{\mathcal{R},u(s,i)}^{k} = {\bold{h}_{\mathcal{R},u(s,i)}^{k}}({\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} {\bold{h}_{\mathcal{R},u(s,i)}^{k}})^{-1}
\end{equation}
Moreover, $BN_0$ denotes the power of Gaussian additive noise, and $I_{u(s,i)}^{k}$ is the power of interfering signals represented as follow
\begin{equation}
\begin{split}
I_{u(s,i)}^{k} &=
 \underbrace{\sum_{\substack{l=1 \\ l\neq i}}^{{U}_{s}} \gamma_{1}  p_{u(s,i)}^{k} |{\bold{h}_{\mathcal{R},u(s,i)}^{H \: k}} \bold{w}_{\mathcal{R},u(s,i)}^{k} |^2}_{\text{(Interference Power)}}\\
&+\underbrace{  \sum_{j=1}^{{R}} {\sigma_q}_{r_j}^2 |\boldsymbol{h}_{r,{u(s,i)}}|^2 a_{u(s,i)}}_{\text{(Quantization Noise Interference)}}
\end{split}
\end{equation}
where $\gamma_{1} = e^{k}_{u(s,i)}e^{k}_{u(s,l)}a_{u(s,i)}a_{u(s,l)}$.
Where $a_{u(s,i)} \in \{0,1\}$ is a binary variable to depict user admission.
$e^{k}_{u(s,i)}$ is the binary variable to show whether the $k^{th}$ PRB is allocated to the UE $i$ in slice $s$, assigned to $r^{th}$ o-RU.

### 2022-01-15 Latex/journal_v1/V4-comp/pr.tex
first commit for new git

Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to assign more than one O-RU to UE.
\caption{Greedy Algorithm for Comp Assignment of O-RU to UEs (GACA)}\label{alg3}
\State Set $\mathtt{R}^{t} = 0$
\State Set $RU = 1$ and  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\For {$s \gets 1$ to $S$}
\State Set $\mathtt{R}^{t} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)} \bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\State $g^{r^*}_{u(s,i)} = 1$ 
\State Set $\mathtt{R} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)}\bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\If{$\mathtt{R} \leq \mathtt{R}^{t}$}
\State Set $g^{r^*}_{u(s,i)} = 0$
\State update $\mathtt{R}^{t}$
\end{enumerate}
\subsection{Iterative Proposed Algorithm}
In \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
Here, the iterative algorithm for the whole problem is demonstrated.
Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using Lagrangian method.  
Afterward, $\boldsymbol{G}$ is updated using GAAOU algorithm. This process is repeated until it converges. 
The whole algorithm is depicted as follow (Algorithm \eqref{alg2}).
\caption{Iterative Algorithm for Power Allocation, PRB, VNF and O-RU Association (IAPPVO)}\label{alg2}
\State  Set the maximum number of iterations ${Iter}_{max}$, convergence condition $\epsilon > 0$ \label{a21}
\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
\For {$i \gets 1$ to $Iter_{max}$}\label{33}
\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
\If {the algorithm converged with the tolerence of $\epsilon$}
\State Break
\State Continue the algorithm  
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

>>>>

We depict $ {\mathfrak{B}}^{rem}_{u_{(s,i)}} \forall s, \forall i$ as a set of O-RUs for each user in each slice. At the beginning of the algorithm, $ {\mathfrak{B}}^{rem}_{u_{(s,i)}} =  \mathcal{R} \forall s, \forall i$. 
Then we assign one O-RU to each UE based on GAAOU algorithm so we guarantee that each UE is assigned to a O-RU. Next, we want to check if we can assign more than one O-RU to UE.

\begin{algorithm}
\caption{Greedy Algorithm for Comp Assignment of O-RU to UEs (GACA)}\label{alg3}
\begin{algorithmic}[1]
\State Set $g^r_{u(s,i)} = 0, \quad \forall s, \forall i, \forall r$.\label{a1}
\State Set $\mathfrak{C}_r = \mathfrak{t}_r, \forall r$  \label{a2}
\State Set ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R}$  $\forall s, \forall i$
\State Set $\mathtt{R}^{t} = 0$
\State Sort slices according to their priority factor ($\delta_s$) in descending order
\For {$s \gets 1$ to $S$}\label{33}
\For {$i \gets 1$ to $U_s$}
\State $RU = 0$
\For {$r \gets 1$ to $R$}
\State Acquire $\mathfrak{G}^r_{u_{(s,i)}} = \bar{\mathcal{R}}^r_{u_{(s,i)}}$
\EndFor
\State \textbf{end for}
\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\While{$RU == 0$}
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$}
\State Set $g^{r^*}_{u(s,i)} = 1$ 
\State Set  $\mathfrak{C}_{r^*} = \mathfrak{C}_{r^*} - \psi_{{r^*},u(s,i)}$
\State Set $RU = 1$ and  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\Else
\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\EndIf
\State \textbf{end if}
\EndWhile
\State \textbf{end while}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for}
\For {$s \gets 1$ to $S$}
\For {$i \gets 1$ to $U_s$}
\State Obtain $r^* = \text{argmax}_{r\in{\mathfrak{B}}^{rem}_{u_{(s,i)}}} \mathfrak{G}^r_{u_{(s,i)}}$
\State  ${\mathfrak{B}}^{rem}_{u_{(s,i)}} = \mathcal{R} \setminus \{{r^*}\} $
\If{$\mathfrak{C}_{r^*} \geq \psi_{r^*,u(s,i)}$} 
\State Set $\mathtt{R}^{t} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)} \bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\State Update $I^{k}_{r,u(s,i)}, \forall s, \forall i$
\State Update $\bar{\mathcal{R}}^{r}_{u_{(s,i)}} \forall s, \forall i$
\State $g^{r^*}_{u(s,i)} = 1$ 
\State Set $\mathtt{R} =\sum_{s=1}^S\sum_{i=1}^{U_s}\sum_{r=1}^{R}\delta_s g^{r}_{u(s,i)}\bar{\mathcal{R}}^{r^*}_{u_{(s,i)}}$
\If{$\mathtt{R} \leq \mathtt{R}^{t}$}
\State Set $g^{r^*}_{u(s,i)} = 0$
\Else
\State update $\mathtt{R}^{t}$
\EndIf
\State \textbf{end if}
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for}
\EndFor
\State \textbf{end for}
\end{algorithmic}
\end{algorithm} 
\end{enumerate}
\subsection{Iterative Proposed Algorithm}
In \eqref{sub1} and \eqref{sub2}, the details of solving each sub-problem are depicted. 
Here, the iterative algorithm for the whole problem is demonstrated.
Firstly, we fixed $\boldsymbol{G}$, then $\boldsymbol{P}$ and $\boldsymbol{E}$ is achieved using Lagrangian method.  
Afterward, $\boldsymbol{G}$ is updated using GAAOU algorithm. This process is repeated until it converges. 
The whole algorithm is depicted as follow (Algorithm \eqref{alg2}).
 \begin{algorithm}
\caption{Iterative Algorithm for Power Allocation, PRB, VNF and O-RU Association (IAPPVO)}\label{alg2}
\begin{algorithmic}[1]
\State  Set the maximum number of iterations ${Iter}_{max}$, convergence condition $\epsilon > 0$ \label{a21}
\State  Assign Users to O-RU randomly (Initialize $\boldsymbol{G}$) \label{a22}
\For {$i \gets 1$ to $Iter_{max}$}\label{23}
\State Acquire $\boldsymbol{P}^{(i)}$, $\boldsymbol{E}^{(i)}$ and $\boldsymbol{M}^{(i)}$ using Lagrangian function and sub-gradient method based on \eqref{sub1}
\State Update $\boldsymbol{G}^{(i)}$   based on algorithm GAAOU \eqref{alg1} in  \eqref{sub2}
\If {the algorithm converged with the tolerence of $\epsilon$}
\State Break
\Else 
\State Continue the algorithm  
\EndIf
\State \textbf{end if}
\EndFor
\State \textbf{end for} \label{24}
\end{algorithmic}
\end{algorithm}
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

### 2022-01-15 Latex/report1/pr.tex
first commit for new git

\section{Network Slicing}
Network slicing, where several logical
networks share a single physical network, has been considered as one of
the key enablers for 5G.

Network slicing is a promising technology for
5G to provide a network as a service (NaaS) for a wide range of
services that run on different virtual networks deployed on a
shared network infrastructure. 
\begin{figure}[h!]
\centering
\includegraphics[scale=0.4]{Capture1.PNG}
\caption{ Big data driven networking}
\label{fig:Bigdata}
\end{figure}
A critical component of network slicing is resource allocation, which needs
to ensure that slices receive the resources needed to support their mobiles/services while optimizing network efficiency.

In a sliced network, network operators
realize the network slices instances to provide the required
network characteristics to different services, pertaining to
third-party tenants.
 Therefore, there will be Service Level
Agreements (SLAs) between network operator and the tenants
to declare the requirements of a particular service and the
operator should fulfill these SLAs via instantiating appropriate
network slices. Requirements of the service instances are
specified in terms of Key Performance Indicators (KPIs), such
as throughput, latency, availability, coverage, etc.

An important aspect of network slicing is to guarantee that
the slices operate independently, i.e., the performance, congestion, failure, etc., in one slice will not negatively influence the
performance of other slices which are sharing the resources.
This means that providing protection from other slices is one
To enable Internet of things (IoT) including high data rate, numerous devices
connection and low service latency,
network slicing and fog computing have been envisioned as
promising solutions in service-oriented 5G architecture.
\begin{figure}[h!]
\centering
\includegraphics[scale=0.5]{Capture.PNG}
\caption{ Service-oriented Architecture of Fog-assisted 5G Network with Network Slicing}
\label{fig:FogNS}
\end{figure}
\section{System Model}
Assume a system model with different types of user equipment (UE).
There exists two different types of
UEs with different requirements: low-latency users (LUs) and
high-data rate Tactile users (TUs).

The first group is very sensitive to the latency. The second group needs high data rate.
Each slice sustains a queue
for the incoming slice traffic, which has a backlog.
%The arrival traffic per slot can be modeled.
The network model is assumed to be composed of a set of M
base stations (BSs).
We have three types of slice resource requirements.
\begin{itemize}
\item A fixed slice requests dedicated radio resources along
time and frequency domains. Therefore, it is isolated
from other slices and does not multiplex its resources
with others. One example is the bandwidth parts (BWPs)
defined in 5G (see 3GPP TS 38.211) that operate on
disjoint parts of the spectrum with a given numerology.
\item A dynamic slice requests a share of resources in terms
of aggregate throughput. It can be mapped to the eMBB
usage scenario, and thus a precise radio resource allocation is less important than the efficient use of available
resources for a guaranteed throughput.
\item An on-demand slice exhibits more stringent requirements
in terms of latency, and hence it can be mapped to
the URLLC scenario. Therefore, such slice should be
assigned radio resources with short delay, in comparison
with the dynamic slice.\citep{schmidt2019slice}
\end{itemize}
\section{introduction}
Network slicing is an important network architecture innovation in 5G that is also expected to be inherited in the next generation. Network slicing enables the coexistence of
multiple isolated and independent virtual (logical) networks,
i.e., slices, on the same physical network infrastructure. The
advantages of network slicing are multifold. First, through the
multiplexing of the virtual networks, network slicing supports
multi-tenancy, i.e., multiple virtual network operators (VNOs)
sharing the same physical network infrastructure. This
reduces capital expense in network deployment and operation. Second, network slicing provides the potential to create customized slices for different service types with various
QoS requirements, which can achieve service differentiation
and guarantee service level agreement (SLA) for each service
type. Third, as slices can be created on-demand and modified
or annulled as needed, network slicing increases the flexibility
and adaptability in network management.

@@

Cooperative Game with Distributed Learning
While existing applications of distributed learning in this field generally consider non-cooperative games where the Nash
equilibriums are achieved, there is a great potential to adopt the concept of cooperative game, where tenants/slices can learn to
make decisions in an organized and cooperative way, in order to maximize the global social welfare instead of their own interests.
In this way, a Pareto optimum can be expected instead of the Nash equilibrium.
\subsection{system model}
In this part, deep reinforcement learning (DRL), which focuses on how to interact with the environment by
trying alternative actions and reinforcing the tendency actions producing more rewarding consequences,
is assumed to be a promising solution for network slicing \cite{drl}.
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{drl}
  \caption{Deep Q learning structure}
  \label{fig:drl}
\end{figure}
Assume we have $V$ services and $S$ slices. Each service needs physical resource blocks (sharing the aggregated bandwidth $W$), RRHs (radio unit head) and CU (control unit) in RAN and VNFs in core (set of requirements $\mathbf{q} = \{q_1, ..., q_{n_v}\}$) and requests specific QoS includes delay, throughput, packetloss, ... . 
So each service $v$ needs specific demands $\mathbf{d} = \{d_1, ..., d_{n_v}\}$.
The target is to maximize long-term reward expectation $E\{R(\mathbf{q},\mathbf{d})\}$
\begin{subequations}
\begin{alignat}{4}
\text{argmax}_{\mathbf{q}} E\{R(\mathbf{q},\mathbf{d})\} \\
\text{subject to} \quad  & \mathbf{q} , \mathbf{d}  
\end{alignat}
\label{constraints1}
\end{subequations}
Set of QoSes $\mathbf{d} = \{d_1, ..., d_{n_v}\}$ includes M/M/1 delays, throughput and packetloss.
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{NS}
  \caption{Network slicing structure \cite{gan}}
  \label{fig:NS}
\end{figure}
\subsubsection{Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_v$ for the  UEs of the $v^{th}$ service.
Therefore, the mean arrival data rate of UEs is
\begin{equation}
D_{v} = \frac{1}{\mu - \lambda_v}.
\end{equation}
where $1/\mu$ is the mean service time and $\lambda$ is the rate of arrival packets.
\subsubsection{Throughput}
Let $\rho_v$ be the mean downlink rate of user $i$ served by service $v$, which
is, for simplicity, defined by Shannon theory as follows
\begin{equation}
\rho_v = w_v log(1+\frac{P_v}{N_v}) 
\end{equation}
where $w_v$ is the bandwidth of service $v$.
\bibliographystyle{plain}
\bibliography{references}
\end{document}

>>>>

\begin{abstract}

\end{abstract}
\begin{IEEEkeywords}

\end{IEEEkeywords}
\section{introduction}
Network slicing is an important network architecture innovation in 5G that is also expected to be inherited in the next generation. Network slicing enables the coexistence of
multiple isolated and independent virtual (logical) networks,
i.e., slices, on the same physical network infrastructure. The
advantages of network slicing are multifold. First, through the
multiplexing of the virtual networks, network slicing supports
multi-tenancy, i.e., multiple virtual network operators (VNOs)
sharing the same physical network infrastructure. This
reduces capital expense in network deployment and operation. Second, network slicing provides the potential to create customized slices for different service types with various
QoS requirements, which can achieve service differentiation
and guarantee service level agreement (SLA) for each service
type. Third, as slices can be created on-demand and modified
or annulled as needed, network slicing increases the flexibility
and adaptability in network management.

@@

 Cooperative Game with Distributed Learning
While existing applications of distributed learning in this field generally consider non-cooperative games where the Nash
equilibriums are achieved, there is a great potential to adopt the concept of cooperative game, where tenants/slices can learn to
make decisions in an organized and cooperative way, in order to maximize the global social welfare instead of their own interests.
In this way, a Pareto optimum can be expected instead of the Nash equilibrium.
\subsection{system model}
In this part, deep reinforcement learning (DRL), which focuses on how to interact with the environment by
trying alternative actions and reinforcing the tendency actions producing more rewarding consequences,
is assumed to be a promising solution for network slicing \cite{drl}.
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{drl}
  \caption{Deep Q learning structure}
  \label{fig:drl}
\end{figure}
Assume we have $V$ services and $S$ slices. Each service needs physical resource blocks (sharing the aggregated bandwidth $W$), RRHs (radio unit head) and CU (control unit) in RAN and VNFs in core (set of requirements $\mathbf{q} = \{q_1, ..., q_{n_v}\}$) and requests specific QoS includes delay, throughput, packetloss, ... . 
So each service $v$ needs specific demands $\mathbf{d} = \{d_1, ..., d_{n_v}\}$.
The target is to maximize long-term reward expectation $E\{R(\mathbf{q},\mathbf{d})\}$
\begin{subequations}
\begin{alignat}{4}
\text{argmax}_{\mathbf{q}} E\{R(\mathbf{q},\mathbf{d})\} \\
\text{subject to} \quad  & \mathbf{q} , \mathbf{d}  
\end{alignat}
\label{constraints1}
\end{subequations}
Set of QoSes $\mathbf{d} = \{d_1, ..., d_{n_v}\}$ includes M/M/1 delays, throughput and packetloss.
\begin{figure}%[H]
  \centering
    \includegraphics[width=\linewidth]{NS}
  \caption{Network slicing structure \cite{gan}}
  \label{fig:NS}
\end{figure}
\subsubsection{Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_v$ for the  UEs of the $v^{th}$ service.
Therefore, the mean arrival data rate of UEs is
\begin{equation}
D_{v} = \frac{1}{\mu - \lambda_v}.
\end{equation}
where $1/\mu$ is the mean service time and $\lambda$ is the rate of arrival packets.
\subsubsection{Throughput}
Let $\rho_v$ be the mean downlink rate of user $i$ served by service $v$, which
is, for simplicity, defined by Shannon theory as follows
\begin{equation}
\rho_v = w_v log(1+\frac{P_v}{N_v}) 
\end{equation}
where $w_v$ is the bandwidth of service $v$.
\bibliographystyle{IEEEtran}
\bibliography{ref}
\end{document}

### 2022-01-15 Latex/tehran-thesis - Copy/tex/chapter1.tex
first commit for new git

\end{itemize}
\section{مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه}
در اینجا به دو مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه می پردازیم. این دو مسئله NP-Hard هستند.
مسئله‌ی NP-hard را نمی توان در زمان چند جمله‌ای حل کرد و نیاز به روش ابتکاری است. در ادامه به بررسی این دو مسئله می‌پردازیم.
\subsection{مسئله‌ی کوله‌پشتی}
یکی از مسائل NP-Hard، مسئله ی کوله پشتی \LTRfootnote{knapsack}
می باشد. در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
هدف در این مسئله قرارگیری بیشترین تعداد اشیاء در این جایگاه‌ها می باشد.
حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد. این مسئله بدین صورت فرمول بندی می‌شود.
\begin{subequations}
	\begin{alignat}{4}
		\max\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{N} p_j x_{j}\\
		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{N} r_{i,j}x_{j} \leq b_i  \quad i =1,...,m, \\
		&\textstyle  x_j \in \{0,1\} \label{eqmain}
	\end{alignat}
	\label{constraints2}
\end{subequations}
که در اینجا، m شرط، شرطهای کوله‌پشتی می‌باشد. در نتیجه این مسئله، کوله‌پشتی mبعدی می‌باشد\cite{chu1998genetic}.
$p_j$
ارزش گزاری شی jام می‌باشد.
همچنین 
برای حل این مسائل از الگوریتمهای branch-and-bound و cutting-plane و الگوریتمهای ابتکاری استفاده می‌شود.
\subsection{مسئله‌ی بسته‌بندی جعبه}
در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می‌باشد.
در مسئله ی بسته بندی جعبه \LTRfootnote{bin packing}
هدف کمینه کردن تعداد جعبه‌های ورودی با فرض اینکه همه‌ی اشیا در آن جا شوند.
حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد. این مسئله بدین صورت فرمول بندی می‌شود.
\begin{subequations}
	\begin{alignat}{4}
		\min\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{n}  y_{j}\\
		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{n}x_{ij} =1  \quad i =1,...,m, \\
		&  \sum_{j=1}^{m} r_{i,j} x_j \leq b_i  \quad i=1,..,m \\
		&  x_{ij} \in \{0,1\}  \quad y_j \in \{0,1\} \quad \forall i,j \label{eqmain}
	\end{alignat}
	\label{constraints2}
\end{subequations}
در اینجا، $y_j$ تعداد جعبه‌های مورد استفاده است که درصورتی که  $\sum_{j=1}^{n}x_{i,j \geq 1}$
باشد، $y_j$ مقدار 1 می‌گیرد و در غیر این صورت 0 است \cite{berkey1987two}.

>>>>

\end{itemize}
\section{مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه}
در اینجا به دو مسئله‌ی کوله‌پشتی و بسته‌بندی جعبه می پردازیم. این دو مسئله NP-Hard هستند.
مسئله‌ی NP-hard را نمی توان در زمان چند جمله‌ای حل کرد و نیاز به روش ابتکاری است. در ادامه به بررسی این دو مسئله می‌پردازیم.
\subsection{مسئله‌ی کوله‌پشتی}
یکی از مسائل NP-Hard، مسئله ی کوله پشتی \LTRfootnote{knapsack}
می باشد. در این مسئله می خواهیم تعدادی شی با وزنهای مختلف را در تعدادی جایگاه با ظرفیت مشخص قرار دهیم.
هدف در این مسئله قرارگیری بیشترین تعداد اشیاء در این جایگاه‌ها می باشد.
حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد. این مسئله بدین صورت فرمول بندی می‌شود.
\begin{subequations}
	\begin{alignat}{4}
		\max\limits_{\boldsymbol{x} }   \quad &   \sum_{j=1}^{N} p_j x_{j}\\
		\text{\lr{subject to}} \quad & \textstyle \sum_{j=1}^{N} r_{i,j}x_{j} \leq b_i  \quad i =1,...,m, \\
		&\textstyle  x_j \in \{0,1\} \label{eqmain}
	\end{alignat}
	\label{constraints2}
\end{subequations}
که در اینجا، m شرط، شرطهای کوله‌پشتی می‌باشد. در نتیجه این مسئله، کوله‌پشتی mبعدی می‌باشد\cite{chu1998genetic}.
$p_j$
ارزش گزاری شی jام می‌باشد.
همچنین 
برای حل این مسائل از الگوریتمهای branch-and-bound و cutting-plane و الگوریتمهای ابتکاری استفاده می‌شود.
\subsection{مسئله‌ی بسته‌بندی جعبه}
در این مسئله هدف قرار دادن تعدادی شیء در تعدادی جعبه با ظرفیت مشخص می‌باشد.
در مسئله ی بسته بندی جعبه \LTRfootnote{bin packing}
هدف کمینه کردن تعداد جعبه‌های ورودی با فرض اینکه همه‌ی اشیا در آن جا شوند.
حل این مسئله با استفاده از روش های مختلف صورت می‌گیرد. این مسئله بدین صورت فرمول بندی می‌شود.
\begin{subequations}
	\begin{alignat}{4}
		\min\limits_{\boldsymbol{x} }   \quad &  K= \sum_{j=1}^{n}  y_{j}\\
		\text{\lr{subject to}} \quad & K\geq 1 \\
		& \sum_{j=1}^{n}x_{ij} =1  \quad i =1,...,m, \\
		&  \sum_{i=1}^{m} r_{i} x_{ij} \leq b_j  \quad j=1,..,n \\
		&  x_{ij} \in \{0,1\}  \quad y_j \in \{0,1\} \quad \forall i,j \label{eqmain}
	\end{alignat}
	\label{constraints2}
\end{subequations}
در اینجا، $y_j$ تعداد جعبه‌های مورد استفاده است که درصورتی که  
$\sum_{i=1}^{n}x_{ij} \geq 1$
باشد، $y_j$ مقدار 1 می‌گیرد 
$x_{ij}$
نشان می‌دهد که شی i در جعبه‌ی j جا دارد.
و در غیر این صورت 0 است \cite{berkey1987two}.
